Stack Safety is a Security Property

### 2021-04-17 tex/main.tex

\paragraph{Formalization of variable passing.}
We add extra information to our call
annotations to reflect that they may now pass variables on the stack, and that the locations
of those variables may be dynamic (as in the case of pass-by-reference).
A call annotation now includes a predicate relating machine states to the components
that should be passed---we can always determine where they should be in terms of their
offsets from the stack pointer, and embed this knowledge in an annotation.

>>>>

\paragraph{Formalization of variable passing.}
We add extra information to our call
annotations to reflect that they may now pass variables on the stack, and that the locations
of those variables may be dynamic (as in the case of pass-by-reference).
A call annotation now includes a predicate relating machine states to the components
that should be passed, expressed as offsets from the stack pointer. \apt{Much better, but the
actual definition of $P$ is still wrong.}
